---
title: "fiddler crab"
format: html
editor: visual
echo: false
---

```{r}
library(lterdatasampler)
library(tidyverse)
library(kableExtra)
```

Creating exploratory plot

This graph shows mean width of Atlantic fiddler marsh crabs by latitude, as measured by the Plum Island Ecosystem LTER monitoring program. Data were collected from salt marshes from Florida to Massachusetts during the summer of 2016.

```{r}
#| fig-cap: "Fiddler Crab size (mm) by latitude in salt marshes"

pie_crab |> 
  ggplot(aes(x = latitude, y = size)) +
  geom_point()
```

```{r}
summary_table <-pie_crab |> 
  group_by(site) |> summarize(mean = round(mean(size, na.rm = TRUE),2), 
                              sd = round(sd(size),2),
                              sample_size = n())

```

This table shows the mean carapace width, standard deviation and sample size for fiddler crabs where width measurements were collected.

```{r}

summary_table |> 
  kable(col.names = c("Site", 
                      "Mean (mm)", 
                      "SD (mm)", 
                      "Sample Size")) |> 
  kable_styling(bootstrap_options = "striped")
```

### Citations

-   Johnson, D. 2019. Fiddler crab body size in salt marshes from Florida to Massachusetts, USA at PIE and VCR LTER and NOAA NERR sites during summer 2016. ver 1. Environmental Data Initiative. <https://doi.org/10.6073/pasta/4c27d2e778d3325d3830a5142e3839bb> (Accessed 2021-05-27).

-   Johnson DS, Crowley C, Longmire K, Nelson J, Williams B, Wittyngham S. The fiddler crab, Minuca pugnax, follows Bergmann's rule. Ecol Evol. 2019;00:1--9. <https://doi.org/10.1002/ece3.5883>

## 
